---
title: "Additional Analysis"
always_allow_html: true
output: 
  html_document:
    toc: true
    code_folding: hide
    toc_float: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(broom)
library(kableExtra)
library(gplots)
library(corrplot)
library(dplyr)
```



### Test Independence between Victim Sex and Suspect Sex

Now we want to test whether there is a relationship between the victim sex and suspect sex, and we are going to use chi-square test.


```{r echo=TRUE, message=FALSE, warning=FALSE}
sex_data = read_csv("./data/nypd_complaint_two_year_data.csv") %>% 
  group_by(vic_sex, susp_sex) %>% 
  summarise(obs = n()) %>% 
  na.omit() %>% 
  pivot_wider(names_from = vic_sex, values_from = obs )

table_sex = sex_data %>% 
  as.matrix() %>% 
  kbl(caption = "Victim Sex Corresponding to Suspect Sex", align = "c") %>% 
  kable_classic(full_width = F, html_font = "Cambria")

table_sex
```

* Ho: sex of victim and sex of suspect are independent
* Ha: sex of victim and sex of suspect are not independent 

```{r echo=TRUE, message=FALSE, warning=FALSE}
matrix_sex =  as.matrix(sex_data) %>% 
  as.integer() %>% 
  na.omit()

chisq.test(matrix_sex)
```


As we can see that the p-value of chi-square test is much smaller than alpha = 0.05, we **reject H0**. 
We can conclude that sex of victim and sex of suspect are *not independent* at 0.05 significance level. 



### Test Independence between Victim Race and Suspect Race

```{r echo=TRUE, message=FALSE, warning=FALSE}
race_data = read_csv("./data/nypd_complaint_two_year_data.csv") %>% 
  group_by(vic_race, susp_race) %>% 
  summarise(obs = n()) %>% 
  na.omit() %>% 
  pivot_wider(names_from = vic_race, values_from = obs)

table_race = race_data %>% 
  as.matrix() %>% 
  kbl(caption = "Victim Race Corresponding to Suspect Race", align = "c") %>% 
  kable_classic(full_width = F, html_font = "Cambria")

table_race
```


* Ho: race of victim and race of suspect are independent
* Ha: race of victim and race of suspect are not independent 


```{r echo=TRUE, message=FALSE, warning=FALSE}
matrix_race =  as.matrix(race_data) %>% 
  as.integer() %>% 
  na.omit()

chisq.test(matrix_race)
```


As we can see that the p-value of chi-square test is much smaller than alpha = 0.05, we **reject H0**. 
We can conclude that race of victim and race of suspect are *not independent* at 0.05 significance level. 

